animbook: Visualizing Changes in Performance Measures and Demographic Affiliations using Animation

### 2025-04-29 animbook-journal.tex
Reviwer 2 page 13

% !TeX root = RJwrapper.tex
\title{animbook: Visualizing changes in performance measures and demographic affiliations using animation}
\author{by Krisanat Anukarnsakulchularp and Dianne Cook}

@@

\abstract{%
Performance is often reported in quantiles or ranks and often repeatedly provided over time. Between elections, voters often switch party preferences, which produces categorical values over time. Inspired by the animation in the New York Times article ``Extensive data show punishing reach of racism for black boys,'' we provide new visualization functions to generate animations that display this type of data in an R package called \CRANpkg{animbook}. Functions to pre-process the data and prepare it for the animation are provided. The methods will be suitable generally for data where categorical variables are measured over time, and provide a way to engagingly view changes.
}

\hypertarget{intro}{%
\section{Introduction}\label{intro}}

The concept of ``zombie companies'' began to attract attention when Caballero, Hoshi, and Kashyap (2008) reported on their proliferation in Japan. Zombie companies are those with an interest coverage ratio of less than one for a period of more than three years, that is, companies taking space in the market but adding no life to the economy. We would detect their presence by a drop in performance, which is a movement pattern in their relative ranking over time. Generally, studying movement patterns is interesting for many problems, including rocket ship start-ups that rapidly perform well or in politics, to study voters who switch party affiliation between elections. Viewing changes between categories over time is an interesting challenge for visualization.

The New York Times provided a possible solution in the article titled ``Extensive data show punishing reach of racism for black boys'' (Badger et al. (2018)) to tell the story of how racism appears to inhibit socioeconomic change. This animation is the motivation for the new visualization presented here to be applied generally.

The challenge in producing an animation like that in the New York Times article animation is the transformation of the data and connection with elements of the plot that will be animated. The complexities include allowing the user to choose the number of categories, standardizing distributions, and allowing the user to input pre-computed categorical data. These considerations provide the objective for creating an R package that can generalize the animation to suitably apply to a wide range of data.

The structure of this paper is as follows. The next section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies. It is followed by sections describing the data format needed, considerations about making animations, and visual design. The software and its functions and usage are detailed in the next section. The next section illustrates the usage of the software to examine company performance, particularly zombie patterns, and the changing political allegiance of voters in Australia. The discussion section summarizes, outlines some limitations, and suggests some future directions.

\hypertarget{NYTvis}{%
\section{Explanation of the New York Times visualization}\label{NYTvis}}

@@

The interactive chart featured in the New York Times article (Figure \ref{fig:nyt}) unveils the issue of income disparities between black and white children who were raised in families with comparable income according to the Chetty et al. (2020). This visualization reveals that, compared to white children, black children are more likely to drop down to the lower-income group, given that they both grew up in wealthy families.

In the visualization, each observation is initially classified into one group at the start and potentially transitions into either the same group or a different group. This dynamics visualization constructs questions on the broader use of this visualization to other types of data. The potential use of this visualization on accounting data is to convey a message, as reported by the McGowan, Andrews, and Millot (2017), that the concept of zombie companies is not unique to Japan alone. It is also present in the United States, which has a faster metabolize rate (more new listings and exits) relative to Japan.

The political data that exhibits the movement of voters switching party affiliations between elections can be a valuable insight into the behavior of the voters. This data could be extended to incorporate demographic information about the voters, providing analysts with a significant insight into voter behavior. This allows them to consolidate effective campaigns for their political party. This also applies to marketing data, where customers shift their product interest to the competitor, providing the marketing analysts with an understanding of both the company's products and the overall market.

This animation was developed using the software based on JavaScript, D3.js (Bostock (2012)), and WebGL (Mozilla Foundation (2011)). The D3 JavaScript is one of the most widely known libraries for creating an interactive and dynamic visualization. It enables the designers to bind both the data and graphical elements to the DOM (Document Object Model). On the other hand, WebGL functions as a JavaScript API for rendering interactive 2D and 3D graphics within any compatible web browser without the use of plug-ins.

Hvitfeldt (2018) provides R (R Core Team (2021)) code to generate an animation similar to that of the New York Times. Taking inspiration from this example, \CRANpkg{animbook} expands upon the visualization in numerous ways and packages the code so that it can be use for a variety of similar animations for studying flow and temporal change data.

The New York Times visualization is also similar to what is called a Sankey plot. Sankey plots are flow diagrams that show the movement/change from one category level to another, with the width of each arrow representing the proportional changes between levels. There are several R packages available to generate versions of Sankey plots, including \CRANpkg{ggalluvial} and \CRANpkg{ggparallel}. The main difference between the Sankey plot visualization and the animation featured in the New York Times lies in their methods of representing the proportion of changes. Sankey plots utilize the width of connecting lines, while the New York Times animation employs the density and color of points.

\hypertarget{data}{%
\section{Data}\label{data}}

@@

In the data structure, there are requirements that must be followed for reproducing the animation. First, the data set needs to be in the \texttt{tidy\ data} format (Wickham (2014)). The data then must have at least ID and time variables, in addition to the measured variables, which would usually be numeric but can also be categorical as well. The ID variable indicates the individual, which is followed over time, such as the company name. There may also be a grouping variable, such as the country where the company is registered.

@@

One of the frequently encountered values in the dataset is NA, commonly known as missing values. In the context of accounting data, NA might signify that a company is either not yet listed or has been de-listed. In scenarios like voter data, NA may indicate that individuals did not provide the necessary information. Disregarding NA values could result in the loss of valuable information. Therefore, instead of completely removing NA entries, this information is categorized into its quantiles, ensuring that the missing data are factored into the visualization.

\hypertarget{animation}{%
\section{Animation tools}\label{animation}}

@@

A principle important for designing a useful animation is called persistence of vision (Webster (2005)). When an image disappears, the brain will retain the previous images for a brief period of time. It is this slight period of retention that allows humans to separate sequential images. If this is seen in quick succession, it will appear as if the objects are in motion. This is illustrated in Figure \ref{fig:animation-diagram}.

There are multiple ways to create an animation in the R environment (R Core Team (2021)), including the packages \CRANpkg{gganimate} (Pedersen and Robinson (2020)) and \CRANpkg{plotly} (Sievert (2020)).

The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package to include the description of an animation. It added new grammar classes to the plot object, allowing it to understand how the plot should change over time. The use of \texttt{transition\_*()} functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time. This includes \texttt{gifski\_renderer()} from the \CRANpkg{gifski} package (Ooms (2023b)) to save animation in GIF format or \texttt{av\_renderer()} from the \CRANpkg{av} package (Ooms (2023a)) to save it into a video file format.

@@

In the context of data, as shown in Figure \ref{fig:animated-diagram}, observations are positioned at specific points in time. The further the distance between these points, the less smooth the animation becomes. This issue can be eliminated by interpolating additional points in between the observations. In the \CRANpkg{gganimate} package, the interpolation is achieved using the \CRANpkg{tweenr} package (Pedersen (2022)), while in \CRANpkg{plotly}, it utilizes d3.interpolate (Bostock (2012)).

Figure \ref{fig:animated-diagram} demonstrates how the frame variables are applied in an animated plot. The frame variable within the animated data structure allows the animation function to determine the position of observations on the plot at any given frame.

From Hasler, Kersten, and Sweller (2007), it suggests that having control options for the animation can improve the efficiency of the learning process. Additionally, the length and speed of the animation should also be taken into consideration. According to R. Mayer (2010), the working memory, responsible for selecting and processing information from sensory memory, only holds a processed version of what was presented for generally less than thirty seconds.

In \CRANpkg{gganimate}, the issue of integrating controls can be addressed by setting the \texttt{renderer} argument to be \texttt{av\_renderer()}, which allows the animation output to be in media applications provided in their systems. As for adjusting the length and speed of the animation, the \texttt{nframes} and \texttt{fps} arguments can be utilized. The \texttt{nframes} dictates the number of frames to be rendered, while \texttt{fps} controls how many frames are displayed in one second. Using these two parameters, the duration of the animation in seconds can be calculated as follows: length = nframes/fps.

@@

\hypertarget{design}{%
\section{Visualization design}\label{design}}

The animated visualization can be an effective communication tool (R. E. Mayer and Moreno (2002); Robertson et al. (2008)). It helps with communicating changing data values, enhancing the narrative, and keeping it engaging for the audience. According to R. E. Mayer and Moreno (2002), animation can improve learning, especially when the goal is to promote deep understanding.

R. E. Mayer (2005) states that designing multimedia requires the designer to understand how people learn. One of the principles in R. E. Mayer (2005), Redundancy, suggests that a piece of excess information could overload the learners. By this principle, the animation must be carefully designed to avoid this pitfall.

@@

The paths of observations are also interpolated to create small changes in the position of points to produce the appearance of motion. The interpolation functions in \CRANpkg{gganimate} and \CRANpkg{plotly} are inadequate because they only generate a linear path. Our animation needs a non-linear path to show the flow. Sigmoid curves are commonly used in Sankey diagrams (Hvitfeldt (2018)). However, Shaffer (2019) argues that a sine curve more accurately represents proportion throughout the path. As illustrated in Figure \ref{fig:proportional-shade}. The sigmoid accurately represents the proportion at the beginning and end, but as it curves, the shape gets narrower, leading to a less accurate proportion representation than the sine curve. New interpolation functions are needed to compute both the sigmoid and sine paths.

\hypertarget{software}{%
\section{Software}\label{software}}

\hypertarget{installation}{%
\subsection{Installation}\label{installation}}

\CRANpkg{animbook} is available through CRAN. The development version of this package can be found in the Github repositories.

@@

\hypertarget{overview-of-functions}{%
\subsection{Overview of functions}\label{overview-of-functions}}

@@

\hypertarget{data-pre-processing}{%
\subsubsection{Data pre-processing}\label{data-pre-processing}}

From Figure \ref{fig:data-diagram}, there is a need to map numerical value to a category. One way to handle this is by ranking the sales and grouping the rankings into quantiles. In some cases, this may not be the best option. When the observation is moved up by quantile, one is bound to move down. This issue can be resolved by using an alternative method, which is grouping values based on their absolute values. Users may also be interested in grouping the data based on different groups, for example, ranking within a specific country. This generalization leads to four different scaling methods for the numerical data.

\begin{verbatim}
#> # A tibble: 12 x 8
#>    id     time gp    values  rank rank_group absolute absolute_group
#>    <fct> <int> <fct>  <dbl> <int>      <int>    <int>          <int>
#>  1 1      2020 X      4255.     3          3        3              3
#>  2 1      2023 X      3357.     2          2        4              4
#>  3 14     2020 X      6763.     2          2        2              2
#>  4 14     2023 X      1197.     4          5        5              5
#>  5 100    2020 X      6864.     2          2        2              2
#>  6 100    2023 X      2321.     3          3        4              4
#>  7 21     2020 Y       698.     5          5        5              5
#>  8 21     2023 Y      3970.     2          2        4              3
#>  9 106    2020 Y      4110.     3          3        3              3
#> 10 106    2023 Y      2866.     3          3        4              4
#> 11 148    2020 Y      7174.     2          2        2              2
#> 12 148    2023 Y      4217.     1          1        3              3
\end{verbatim}

@@

@@

All of these scaling methods utilized the \texttt{cut()} function from the base R package (R Core Team (2021)) to split the values into quantiles. The \texttt{cut()} function requires the specification of the \texttt{breaks} argument. If it is not provided, the prep function in this package defaults to using the \texttt{seq()} function, which sets the minimum and maximum values to 0 and 1, respectively, and then increments by equal steps based on the number of groups of interest. Additionally, the users have the option to specify the breaks themselves if they choose to do so, noting that the breaks provided need to be between 0 and 1, and the length of the vector needs to be the number of groups plus 1.

@@

These are only the initial steps in formatting the data into a category. Now that there is a method to transform the data from the raw into a categorized format, the next step is to modify it into an animated data structure. It is carried out by assigning the frame to each individual observation, ensuring that each ID does not contain repeat frame values. It lets the \CRANpkg{gganimate} or \CRANpkg{plotly} perceive where the observation would be on the plot at a given frame, as seen in Figure \ref{fig:animated-diagram}.

The frame variable is assigned by sorting the data based on the ID and time using the \texttt{arrange()} function, followed by applying the \texttt{group\_by()} function on the ID, allowing the \texttt{row\_number()} function to be performed within each group. The functions mentioned in this paragraph are from the \CRANpkg{dplyr} package (Wickham et al. (2023)). These are done by the internal function for each of the plots provided in the packages.

@@

The argument for the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()} function are listed in the Table \ref{tab:tbl-num-la} and \ref{tab:tbl-cat-la} respectively. The \texttt{data}, \texttt{id}, \texttt{values}, and \texttt{time} arguments are required for both functions.

@@

\hypertarget{plotting-function}{%
\subsubsection{Plotting function}\label{plotting-function}}

Once the data is prepared. The next step is to create the \texttt{ggplot} object as a basis for the animation. There are three plots available in this package. Two of the plots could be used for the animation, and another plot is used as a static visualization. All of the plots have an internal function that converts the categorized data format into the animated structure for each plotting function.

@@

The \texttt{wallaby\_data()} function is responsible for performing data manipulation and formatting tasks on the original object. It includes creating additional data components for labeling and shading. This function also responds by interpolating the non-linear path. It performs this task by mapping the \texttt{sine()} function provided in this package to each observation using the \texttt{map()} function from the \CRANpkg{purrr} package (Wickham and Henry (2023)). The frame is recalculated using the same method mentioned in the data preprocessing section. The \texttt{proportional\_shade()} function is called to generate the proportional shaded data.

@@

\hypertarget{animating-function}{%
\subsubsection{Animating function}\label{animating-function}}

It is necessary to save the plot as a \texttt{ggplot} object before passing it to the final function, \texttt{anim\_animate()}, to animate. This function will automatically detect which rendering method was specified in the previous steps and add the minimum requirement functions accordingly. By default, if the user specifies the rendering as \texttt{gganimate}, then it will add the \texttt{transition\_time()} function from the \CRANpkg{gganimate} package. Otherwise, the \texttt{animation\_opts()} function will be added from the \CRANpkg{plotly} package.

\hypertarget{example-usage}{%
\subsection{Example usage}\label{example-usage}}

The \texttt{cat\_change} data in the package is used to illustrate how to use this package. It has five categories, A to E, over two-time points. Since the data is already in the categorized data structure, the \texttt{anim\_prep\_cat()} function is used. The output from this function is a class called \texttt{categorized}.

@@

\hypertarget{applications}{%
\section{Applications}\label{applications}}

Two examples of usage are provided. The osiris example studies company movement between quartiles of sales performance over a 12-year period. The voting example studies party preference changes between 2016 and 2019 elections.

\hypertarget{accounting-database-osiris}{%
\subsection{Accounting database: osiris}\label{accounting-database-osiris}}

The Osiris data presented in this section was acquired from Bureau van Dijk ({``Osiris''} (2023)), compiling information on a total of 122,318 companies. It was subsequently a subset for the 2021 report, consisting of 1000 companies with 94 variables. The dataset included in the package focuses on 790 companies, spanning from 2006 to 2018. The variables in this dataset include year, ID, country, sales, and japan.

McGowan, Andrews, and Millot (2017) reported that companies in the United States have a faster metabolic rate relative to Japanese companies. This means that US companies tend to move up and down performance metrics more frequently than Japanese companies. This can be examined using the wallaby and kangaroo plots. The wallaby plot allows the study of entry and exit behavior. The kangaroo plot allows for studying the full movement of companies over time.

@@

In the kangaroo plot (Figure \ref{fig:kan-osiris-figure}) the five grey bars indicate the five categories (Top 25\%, 25-50, 50-75, 75-100, Not listed) across years 2006 and 2018. Points represent individual companies with color indicating the country of registration. Points that stay within the bar indicate companies that remain in the same quartile over the entire time period. If a company drops in performance or improves performance to the extent of switching quartile, the corresponding point will jump up or down in this plot. Note that all the companies in the ``Not listed'' category were listed at some point during this time period. It can be seen that most companies stay in the same quantile group over the time period. There are several companies that move up and down, and most of these are US companies. This supports the McGowan, Andrews, and Millot (2017) claim that US companies have a higher turnover rate compared to Japanese companies.

@@

In Figure \ref{fig:osiris-figure}, the focus is placed on companies that exited the market in 2018 that were in the market at some point since 2006. The grey regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018. (explain the difference in proportion and not listed companies). In 2006, the companies represented by points, colored by country, were in one of the quartiles or ``Not listed'' category. All the companies in the Top 25\% were US companies. Any Japanese companies in the Top 25\% in 2006 did not exit the market (Not listed). But actually, there were non-Japanese companies in the Top 25\% in 2006. It is also interesting that the larger proportion of the companies in the Top 25\% are getting de-listed, and the lower the quartiles, the less likely that the companies will exit the market.

@@

\hypertarget{voter-behavior}{%
\subsection{Voter behavior}\label{voter-behavior}}

The election survey dataset included in the \CRANpkg{animbook} package focuses on the voter behavior of the 734 individuals who participated in the 2019 survey. The variables in this data are id, year, party, and gender. The ID variable has been de-identified to ensure the privacy of the responders, preventing the identification of the survey participants. The year column is derived from the two different questions in the survey, which answered how the top party performs in keeping the old voters of different genders relative to the 2016 Australian election results. This dataset was collected from ADA Dataverse (McAllister et al. (2023)).

@@

According to the survey ({``{LGBTIQ+ Health Australia Party survey}''} (2022)), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities. However, the Labor Party only gives a broad statement of commitment to a range of LGBTIQ+ and human rights issues. This includes working with LGBTIQ+ Australians and advocates to ensure equality before the law and full access to Medicare.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{acknowledgements}{%
\section*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{section}{Acknowledgements}

>>>>

% !TeX root = RJwrapper.tex
\title{animbook: Visualizing Changes in Performance Measures and Demographic Affiliations using Animation}

\author{by Krisanat Anukarnsakulchularp and Dianne Cook}

@@

\abstract{%
Performance is often reported in quantiles or ranks and often repeatedly provided over time. Between elections, voters often switch party preferences, which produces categorical values over time. Inspired by the animation in the New York Times article ``Extensive data show punishing reach of racism for black boys,'' we provide new visualization functions to generate animations that display this type of data in an R package called animbook. Functions to pre-process the data and prepare it for the animation are provided. The methods will be suitable generally for data where categorical variables are measured over time, and provide a way to engagingly view changes.
}

\section{Introduction}\label{intro}

The concept of ``zombie companies'' began to attract attention when \citet{zombie_companies_2008} reported on their proliferation in Japan. Zombie companies are those with an interest coverage ratio of less than one for a period of more than three years, that is, companies taking space in the market but adding no life to the economy. We would detect their presence by a drop in performance, which is a movement pattern in their relative ranking over time. Generally, studying movement patterns is interesting for many problems, including rocket ship start-ups that rapidly perform well or in politics, to study voters who switch party affiliation between elections. Viewing changes between categories over time is an interesting challenge for visualization.

The New York Times provided a possible solution in the article titled ``Extensive data show punishing reach of racism for black boys'' (\citet{the_new_york_time}) to tell the story of how racism appears to inhibit socioeconomic change represent using the animation showing an individual transition from one category to another. This animation is the motivation for the new visualization presented here to be applied generally.

The challenge in producing an animation similar to the New York Times article animation is the transformation of the data and connection with elements of the plot that will be animated. The complexities include allowing the user to choose the number of categories, standardizing distributions, and allowing the user to input pre-computed categorical data. These considerations provide the objective for creating an R package that can generalize the animation to suitably apply to a wide range of data.

The structure of this paper is as follows. The subsequent section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies. It is then followed by sections describing the data format needed, considerations about making animations, and visual design. The functions and usage of the software are detailed in the next section. Just prior to the final section, the paper illustrates the usage of the software to examine company performance, particularly zombie patterns, and the changing political allegiance of voters in Australia. The concluding discussion section summarizes, outlines some limitations, and suggests future directions for the software.

\section{Explanation of the New York Times visualization}\label{NYTvis}

@@

The interactive chart featured in the New York Times article (Figure \ref{fig:nyt}) unveils the issue of income disparities between black and white children who were raised in families with comparable income according to \citet{race}. This visualization reveals that, compared to white children, black children are more likely to drop down to the lower-income group, given that they both grew up in wealthy families.

In the visualization, each observation is initially classified into one group at the start and potentially transitions into either the same group or a different group. This dynamic visualization constructs questions on the broader use of this visualization to other types of data. The potential use of this visualization on accounting data is to convey a message, as reported by \citet{oecd_report}, that the concept of zombie companies is not unique to Japan alone. It is also present in the United States, which has a faster metabolization rate (more new listings and exits) relative to Japan.

The political data that exhibits the movement of voters switching party affiliations between elections can be a valuable insight into the behavior of the voters. This data could be extended to incorporate demographic information about the voters, providing analysts with significant insight into voter behavior and allowing them to consolidate effective campaigns for their political party. It can also be applied to marketing data, where customers shift their product interest to the competitor, providing the marketing analysts with an understanding of both the company's products and the overall market.

This animation was developed using software based on JavaScript, D3.js (\citet{d3js}), and WebGL (\citet{webgl}). The D3 JavaScript is one of the most widely known libraries for creating an interactive and dynamic visualization. It enables the designers to bind both the data and graphical elements to the DOM (Document Object Model). On the other hand, WebGL functions as a JavaScript API for rendering interactive 2D and 3D graphics within any compatible web browser without the use of plug-ins.

\citet{Hvitfeldt_2018} provides R (\citet{r}) code to reproduce an animation similar to that of the New York Times. Taking inspiration from this coding example, \CRANpkg{animbook} expands upon the visualization in numerous ways and packages the code so that it can be used for a variety of similar animations for studying flow and temporal change data.

The New York Times visualization is similar to a Sankey plot. Sankey plots are flow diagrams that show the movement/change from one category level to another, with the width of each arrow representing the proportional changes between levels. There are several R packages available to generate versions of Sankey plots, including \CRANpkg{ggalluvial} and \CRANpkg{ggparallel}. The main difference between the Sankey plot visualization and the animation featured in the New York Times lies in their methods of representing the proportion of changes. Sankey plots utilize the width of connecting lines, while the New York Times animation employs the density and color of points.

\section{Data}\label{data}

@@

In the data structure, there are requirements that must be followed for reproducing the animation. First, the dataset needs to be in a \texttt{tidy\ data} format (\citet{tidy-data}). The data then must have at least ID and time variables, in addition to the measured variables, which would usually be numeric but can also be categorical as well. The ID variable indicates the individual, which is followed over time, such as the company name. There may also be a grouping variable, such as the country where the company is registered (United States and Japan).

@@

One of the frequently encountered values in the dataset is NA, commonly known as a missing value. In the context of accounting data, NA might signify that a company is either not yet listed or has been de-listed. In scenarios like voter data, NA may indicate that individuals did not provide the necessary information. Disregarding NA values could result in the loss of valuable information. Therefore, instead of completely removing NA entries, it will get converted into its own quantiles, ensuring that the missing data are factored into the visualization.

\section{Animation tools}\label{animation}

@@

An principle important for designing a useful animation is called persistence of vision (\citet{animation-mechanic}). When an image disappears, the brain will retain the previous images for a brief period of time. It is this slight period of retention that allows humans to separate sequential images. If this is seen in quick succession, it will appear as if the objects are in motion. This is illustrated in Figure \ref{fig:animation-diagram}. There are multiple ways to create an animation in the R environment (\citet{r}), including the packages \CRANpkg{gganimate} (\citet{gganimate}) and \CRANpkg{plotly} (\citet{plotly}).

The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package (\citet{ggplot2}) to include the description of an animation. It added new grammar classes to the plot object, allowing it to understand how the plot should change over time. The use of \texttt{transition\_*()} functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time. The \CRANpkg{gganimate} includes \texttt{gifski\_renderer()} from the \CRANpkg{gifski} package (\citet{gifski}) to save animation in GIF format or \texttt{av\_renderer()} from the \CRANpkg{av} package (\citet{av}) to save it into a video file format.

@@

Figure \ref{fig:animated-diagram} demonstrates how the frame variables are applied in an animated plot. The frame variable within the animated data structure allows the animation function to determine the position of observations on the plot at any given frame. These observations are positioned at specific points in time. The further the distance between these points, the less smooth the animation becomes. This issue can be eliminated by interpolating additional points in between the observations. In the \CRANpkg{gganimate} package, the interpolation is achieved using the \CRANpkg{tweenr} package (\citet{tweenr}), while in \CRANpkg{plotly}, it utilizes d3.interpolate (\citet{d3js}).

From \citet{learner-control}, it suggests that having control options for the animation can improve the efficiency of the learning process. Additionally, the length and speed of the animation should also be taken into consideration. According to \citet{mayer-2010}, the working memory, responsible for selecting and processing information from sensory memory, only holds a processed version of what was presented for generally less than thirty seconds.

In \CRANpkg{gganimate}, the issue of integrating controls can be addressed by setting the \texttt{renderer} argument to be \texttt{av\_renderer()}, which allows the animation output to be in media applications provided in their systems. As for adjusting the length and speed of the animation, the \texttt{nframes} and \texttt{fps} arguments can be utilized. The \texttt{nframes} dictate the number of frames to be rendered, while \texttt{fps} controls how many frames are displayed in one second. Using these two parameters, the duration of the animation in seconds can be calculated as follows: length = nframes/fps.

@@

\section{Visualization design}\label{design}

The animated visualization can be an effective communication tool (\citet{Mayer_Moreno_2002}; \citet{effective-trend}). It helps with communicating changing data values, enhancing the narrative, and keeping it engaging for the audience. According to \citet{Mayer_Moreno_2002}, animation can improve learning, especially when the goal is to promote deep understanding.

\citet{mayer_2005} states that designing multimedia requires the designer to understand how people learn. One of the principles in \citet{mayer_2005}, Redundancy, suggests that a piece of excess information could overload the learners. By this principle, the animation must be carefully designed to avoid this pitfall.

@@

The paths of observations are also interpolated to create small changes in the position of points to produce the appearance of motion. The interpolation functions in \CRANpkg{gganimate} and \CRANpkg{plotly} are inadequate because they only generate a linear path. Our animation needs a non-linear path to show the flow. Sigmoid curves are commonly used in Sankey diagrams (\citet{Hvitfeldt_2018}). However, \citet{Shaffer_2019} argues that a sine curve more accurately represents proportion throughout the path. As illustrated in Figure \ref{fig:proportional-shade}, the sigmoid accurately represents the proportion at the beginning and end, but as it curves, the shape gets narrower, leading to a less accurate proportion representation than the sine curve. New interpolation functions are needed to compute both the sigmoid and sine paths.

\section{Software}\label{software}

\subsection{Installation}\label{installation}

\CRANpkg{animbook} is available through CRAN. The development version of this package can be found in the GitHub repositories at \url{https://github.com/KrisanatA/animbook}.

@@

\subsection{Overview of functions}\label{overview-of-functions}

@@

\subsubsection{Data pre-processing}\label{data-pre-processing}

From Figure \ref{fig:data-diagram}, there is a need to map numerical value to a category. One way to handle this is by ranking the observation and grouping the rankings into quantiles. In some cases, this may not be the best option because when an observation is moved up by a quantile, another one is bound to move down, making the amount of observation in the quantile remain the same. This issue can be resolved by using an alternative method, which is grouping values based on their absolute values. Users may also be interested in grouping the data based on different groups, for example, ranking within a specific country. This generalization leads to four different scaling methods for the numerical data.

@@

\caption{\label{tab:tbl-scaling-la}A summary of different scaling methods applied to the dataset.}
\centering
\begin{tabular}[t]{l|>{\raggedleft\arraybackslash}p{30em}|l|r|r|r|r|r}
\hline
id & time & gp & values & rank & rank\_group & absolute & absolute\_group\\
\hline
1 & 2020 & X & 4254.6677 & 3 & 3 & 3 & 3\\
\hline
1 & 2023 & X & 3357.0312 & 2 & 2 & 4 & 4\\
\hline
14 & 2020 & X & 6763.4772 & 2 & 2 & 2 & 2\\
\hline
14 & 2023 & X & 1197.4183 & 4 & 5 & 5 & 5\\
\hline
100 & 2020 & X & 6864.4950 & 2 & 2 & 2 & 2\\
\hline
100 & 2023 & X & 2321.3183 & 3 & 3 & 4 & 4\\
\hline
21 & 2020 & Y & 698.2479 & 5 & 5 & 5 & 5\\
\hline
21 & 2023 & Y & 3970.0503 & 2 & 2 & 4 & 3\\
\hline
106 & 2020 & Y & 4109.6530 & 3 & 3 & 3 & 3\\
\hline
106 & 2023 & Y & 2865.6471 & 3 & 3 & 4 & 4\\
\hline
148 & 2020 & Y & 7173.7712 & 2 & 2 & 2 & 2\\
\hline
148 & 2023 & Y & 4217.4130 & 1 & 1 & 3 & 3\\
\hline
\end{tabular}
\end{table}

@@

All of these scaling methods utilized the \texttt{cut()} function from the base R package (\citet{r}) to split the values into quantiles. The \texttt{cut()} function requires the specification of the \texttt{breaks} argument. If it is not provided, the prep function in this package defaults to using the \texttt{seq()} function, which sets the minimum and maximum values to 0 and 1, respectively, and then increments by equal steps based on the number of groups of interest. Additionally, the users have the option to specify the breaks themselves if they choose to do so, noting that the breaks provided need to be between 0 and 1, and the length of the vector needs to be the number of groups plus 1.

@@

These are only the initial steps in formatting the data into a category. Now that there is a method to transform the data from the raw into a categorized format, the next step is to modify it into an animated data structure. It is carried out by assigning a frame to each individual observation, ensuring that each ID does not contain repeated frame values. It lets the \CRANpkg{gganimate} or \CRANpkg{plotly} perceive where the observation would be on the plot at a given frame, as seen in Figure \ref{fig:animated-diagram}.

The frame variable is assigned by sorting the data based on the ID and time using the \texttt{arrange()} function, followed by applying the \texttt{group\_by()} function on the ID, allowing the \texttt{row\_number()} function to be performed within each group. The functions mentioned in this paragraph are from the \CRANpkg{dplyr} package (\citet{dplyr}). These are done by the internal function for each of the plots provided in the packages.

@@

The arguments for the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()} functions are listed in Tables \ref{tab:tbl-num-la} and \ref{tab:tbl-cat-la} respectively. The \texttt{data}, \texttt{id}, \texttt{values}, and \texttt{time} arguments are required for both functions.

@@

\subsubsection{Plotting function}\label{plotting-function}

Once the data is prepared. The next step is to create the \texttt{ggplot} object as a basis for the animation. There are three plots available in this package. Two of the plots could be used for the animation, and another plot is used as a static visualization. All of each plot has an associated internal function that converts the categorized data format into the animated structure.

@@

The \texttt{wallaby\_data()} function is responsible for performing data manipulation and formatting tasks on the original object. It includes creating additional data components for labeling and shading. This function is also responsible for interpolating the non-linear path. It performs this task by mapping the \texttt{sine()} function provided in this package to each observation using the \texttt{map()} function from the \CRANpkg{purrr} package (\citet{purrr}). The frame is recalculated using the same method mentioned in the data preprocessing section. The \texttt{proportional\_shade()} function is called to generate the proportional shaded data.

@@

\subsubsection{Animating function}\label{animating-function}

It is necessary to store the plot as a \texttt{ggplot} object before passing it to the final function, \texttt{anim\_animate()}, to animate. This function will automatically detect which rendering method was specified in the previous steps and add the minimum requirement functions accordingly. By default, if the user specifies the rendering as \texttt{gganimate}, then it will add the \texttt{transition\_time()} function from the \CRANpkg{gganimate} package. Otherwise, the \texttt{animation\_opts()} function will be added from the \CRANpkg{plotly} package.

\subsection{Example usage}\label{example-usage}

The \texttt{cat\_change} data in the package is used to illustrate how to use this package. It has five categories, A to E, over two time points. Since the data is already in the categorized data structure, the \texttt{anim\_prep\_cat()} function is used. The output from this function is a class called \texttt{categorized}.

@@

\section{Applications}\label{applications}

Two real-world examples of usage are provided. The osiris example studies company movement between quartiles of sales performance over a 12-year period. The voting example studies party preference changes between the 2016 and 2019 elections.

\subsection{Accounting database: osiris}\label{accounting-database-osiris}

The Osiris data presented in this section was acquired from Bureau van Dijk (\citet{bvd}), compiling information on a total of 122,318 companies. It was subsequently subsetted for the 2021 report, consisting of 1000 companies with 94 variables. The dataset included in the package focuses on 790 companies, spanning from 2006 to 2018. The variables in this dataset include year, ID, country, sales, and japan.

\citet{oecd_report} reported that companies in the United States have a faster metabolic rate relative to Japanese companies. This means that US companies tend to move up and down in the performance metrics more frequently than Japanese companies. This can be examined using the wallaby and kangaroo plots. The wallaby plot allows the study of entry and exit behavior. The kangaroo plot allows for studying the full movement of companies over time.

@@

In the kangaroo plot (Figure \ref{fig:kan-osiris-figure}) the five gray bars indicate the five categories (Top 25\%, 25-50, 50-75, 75-100, Not listed) across years 2006 and 2018. Points represent individual companies with color indicating the country of registration. Points that stay within the bar indicate companies that remain in the same quartile over the entire time period. If a company drops in performance or improves performance to the extent of switching quartile, the corresponding point will jump up or down in this plot. Note that all the companies in the ``Not listed'' category were listed at some point during this time period. It can be seen that most companies stay in the same quantile group over the time period. There are several companies that move up and down, and most of these are US companies. This supports the \citet{oecd_report} claim that US companies have a higher turnover rate compared to Japanese companies.

@@

In Figure \ref{fig:osiris-figure}, the focus is placed on companies that exited the market in 2018 that were in the market at some point since 2006. The gray regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018. (explain the difference in proportion and not listed companies). In 2006, the companies represented by points, colored by country, were in one of the quartiles or ``Not listed'' category. All the companies in the Top 25\% were US companies. Any Japanese companies in the Top 25\% in 2006 did not exit the market (Not listed). It is worth noting that there are actually none of the Japanese companies in the Top 25\% in 2006. It is also interesting that the larger proportion of the companies in the Top 25\% are getting de-listed, and the lower the quartiles, the less likely that the companies will exit the market.

@@

\subsection{Voter behavior}\label{voter-behavior}

The election survey dataset included in the \CRANpkg{animbook} package focuses on the voter behavior of the 734 individuals who participated in the 2019 survey. The variables in this data are id, year, party, and gender. The ID variable has been de-identified to ensure the privacy of the responders, preventing the identification of the survey participants. The year column is derived from the two different questions in the survey, which answered how the top party performs in keeping the old voters of different genders relative to the 2016 Australian election results. This dataset was collected from ADA Dataverse (\citet{aeles}).

@@

According to the survey (\citet{lgbtiq}), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities. However, the Labor Party only gives a broad statement of commitment to a range of LGBTIQ+ and human rights issues. This includes working with LGBTIQ+ Australians and advocates to ensure equality before the law and full access to Medicare.

\section{Discussion}\label{discussion}

@@

\section*{Acknowledgements}\label{acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}
